### 2018-09-20 VV556/HW1/submission.tex
ex1 ok
add ex3

%----------------------------------------------------------------------------------------
%	PROBLEM 1
%----------------------------------------------------------------------------------------

\section{Metric Space}

%----------------------------------------------------------------------------------------
%	PROBLEM 2
%----------------------------------------------------------------------------------------

\section{Continuity}

%----------------------------------------------------------------------------------------
%	PROBLEM 3
%----------------------------------------------------------------------------------------

\section{Cardinalty}

>>>>

\section{Exercise1.1}
\begin{enumerate}
	\item 
		\begin{equation}
			\dim{U} = 2
		\end{equation}
		As there are 4 components within $x$, and 2 constraints.
	\item 
		\begin{equation}
			\dim{U} = 3
		\end{equation}
		As there are 4 components within $x$, and 1 constraint.
	\item 
		\begin{equation}
			\begin{aligned}
				\dim{U+V} & = \dim{U} + \dim{V} - \dim{U \cap V} \\
				          & = 2 + 3 - 2 \\
				          & = 3
			\end{aligned}
		\end{equation}
		The dimension of $U \cap V$ can be observed from
		\begin{equation}
			\begin{aligned}
				U \cap V & = \{x\in \mathbb{R}^4| x_1 + x_2 + x_3 = 0, x_1 + 3 x_2 = x_4, x_1 = x_4\}\\
				         & = \{x\in \mathbb{R}^4| x_2 = 0, x_1 + x_3 = 0\}
			\end{aligned}
		\end{equation}
\end{enumerate}

\section{Exercise1.2}
\begin{enumerate}
	\item
		The pointwise limit is given as follows
		\begin{equation}
			f = \left\{\begin{aligned}
			0, & x = 0\\
			1, & x\in(0,1]
			\end{aligned}
			\right.
		\end{equation}
		It's of uniform convergence as
		\begin{equation}
			\begin{aligned}
				&  \lim\limits_{n\rightarrow\infty} \sup_{x\in[0, 1]} |f_n(x) - f(x)|\\
				&=\left\{
					\begin{aligned}
						&0,  &x=0\\ 
						&\lim\limits_{x\rightarrow 0,  n \rightarrow \infty} |x^{\frac{1}{n}} - 1|, & x \in (0, 1]
					\end{aligned}
					\right.\\
				&=0
			\end{aligned}
		\end{equation}
	\item 
		The pointwise limit is given as
		\begin{equation}
			f(x) = x
		\end{equation}
		It's not of uniform convergence.
	\item 
		The pointwise limit is given as
		\begin{equation}
			f(x) = 0
		\end{equation}
		It's of uniform convergence as
		\begin{equation}
			\begin{aligned}
				&	\lim\limits_{n\rightarrow\infty}\sup_{x\in(0, \infty)}|f_n(x) - f(x)|\\
				& =\lim\limits_{n\rightarrow\infty}\sup_{x\in(0, \infty)}\Biggl|\sqrt{\frac{1}{n} + x} - \sqrt{x}\Biggr|\\
				& =\lim\limits_{n\rightarrow\infty}\sup_{x\in(0, \infty)}\Biggl|\frac{1}{n(\sqrt{\frac{1}{n} + x} + \sqrt{x})}\Biggr|\\
				& = \lim\limits_{n\rightarrow\infty, x \rightarrow 0}\frac{1}{n(\sqrt{\frac{1}{n} + x} + \sqrt{x})}\\
				& = \lim\limits_{n\rightarrow\infty, x \rightarrow 0}\frac{1}{2n\sqrt{x}} = 0
			\end{aligned}
		\end{equation}
\end{enumerate}

\section{Exercise1.3}
	\begin{enumerate}
		\item 
			Not figured out...
		\item 
			For example
			\begin{equation}
				a_n = \frac{1}{n}
			\end{equation}
		\item 
			Consider a sequence constructed as follows
			\begin{equation}
				\begin{aligned}
					& x_1 = \frac{1}{1} & (1^1=1 \ item)\\
					& x_2 = ... = x_5 = \frac{1}{2} & (2^2=4 \ items)\\
					& x_6 = ... = x_{32} = \frac{1}{3} & (3^3=27 \ items)\\
					& ...
				\end{aligned}
			\end{equation}
			This sequence certainly converges to 0. But not in $L^p$ for any $p>=1$ as
			\begin{equation}
				\sum_{n=1}^{\infty} = 1 + \frac{2^2}{2^p} + \frac{3^3}{3^p} + ... + \frac{n^n}{n^p} + ...
			\end{equation}
			for any $n > p$, $\frac{n^n}{n^p} > 1$.
	\end{enumerate}
